Analysis and figures

### 2025-03-04 Analysis.qmd
Major changes to MS over the past two weeks prior to resubmission

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("#4D7668", "gray50")) +
  scale_y_continuous(expand = c(0,0), limits = c(0, 65)) +
  scale_x_continuous(#limits = seq(2004, 2023, 1),
                     breaks = seq(2004, 2023, 4),
                     labels = seq(2004, 2023, 4)) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-5,-10),
        legend.position = "top", 
        legend.key.size = unit(10, 'points'),
        legend.direction = "vertical",
        axis.text.y = element_text(size = 8, family = "helvetica", colour = "#585858"),
        axis.text.x = element_text(size = 8, family = "helvetica", 
                                   colour = "#585858", angle = 60,
                                   vjust = 1, hjust = 1), 
        axis.title = element_text(size = 8, family = "helvetica", colour = "#585858"), 
        legend.text = element_text(size = 8, family = "helvetica", colour = "#585858"),
        strip.text.x = element_text(size = 8, family = "helvetica", colour = "#585858"))
#+ facet_grid(cols = vars(Strata), scales = "free_x", switch = "x")
plot_reviewCoverage
ggsave(plot = plot_reviewCoverage, "Figures/CoveragePlot.png",
       width = 945, height = 700, units = "px")
```

@@

ggsave("Figures/StudiesMap.eps", plot = plot_studyAreaMap,
       width = 85, height = 50, units = "mm", bg = "transparent")

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "#4D7668", colour = "white",
           width = 1, linewidth = .5) +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("< 1", "1 - 10", "10 - 10<sup>2</sup>",
                              "10<sup>2</sup> - 10<sup>3</sup>",
                              "10<sup>3</sup> - 10<sup>4</sup>",
                              "10<sup>4</sup> - 10<sup>5</sup>",
                              "10<sup>5</sup> - 10<sup>6</sup>",
                              "\\> 10<sup>6</sup>")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_markdown(size = 8, angle = 90,
                                       vjust = 0.5, hjust = 1,
                                       family = "Helvetica"),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
plot_studyAreaSize

ggsave("Figures/StudyAreaPlot.eps",
       plot = plot_studyAreaSize, 
       width = 80, height = 45, units = "mm",
       bg='transparent')
```

@@

ggsave("Figures/TaxaPlot.eps",
       plot_focalTaxa, width = 90, height = 40, units = "mm",
       bg = "transparent")
```

@@

# Plot site quantity distribution
plot_siteQuantity <- sheet_DataCollection |>
  filter(`Site quantity` != "Unclear") |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(x = `Site quantity`),
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  scale_x_continuous(transform = "log10",
                     breaks = c(0, 10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 7500),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  labs(y = "Number of\nsites", x = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent',
                                        color = NA),
        plot.background = element_rect(fill = 'transparent', 
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   #vjust = .5,
                                   hjust = 1,
                                   colour = "#585858",
                                   family = "Helvetica"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.margin = margin(20,10,0,10),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                   family = "Helvetica"))
plot_siteQuantity
ggsave(plot = plot_siteQuantity, 
       filename = "Figures/Sites.eps",
       height = 35, width = 110, units = "mm")

@@

  ggplot() +
  geom_histogram(aes(x = StudyMonths), 
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(StudyMonths, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  labs(x = "", y = "Study\nduration") +
  scale_x_continuous(transform = "log10",
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years"),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent', 
                                        color = NA),
        plot.background = element_rect(fill = 'transparent',
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   hjust = 1, 
                                   family = "Helvetica",
                                   colour = "#585858"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                    family = "Helvetica"),
        plot.margin = margin(20,10,0,10))
plot_studyDuration
ggsave(plot = plot_studyDuration, 
       filename = "Figures/Duration.eps",
       height = 35, width = 110, units = "mm",
       bg = "transparent")

# Calculate sample size
stat_studyDurationN <- sheet_DataCollection |>
  filter(`Start month` != "Unclear" & `End month` != "Unclear") |>
  nrow()
stat_studyDurationN
```

We combine the study duration figure and the site quantity figure using `patchwork`.

```{r combine sites and duration}
#| fig-width: 12
#| fig-height: 7.5

plot_combinedStudyScale <- plot_siteQuantity / plot_spacer() / plot_studyDuration
plot_combinedStudyScale <- plot_combinedStudyScale +
  theme(panel.background = element_rect(fill='transparent', color = NA),
        plot.background = element_rect(fill='transparent', color = NA))
plot_combinedStudyScale
ggsave(plot = plot_combinedStudyScale, filename = "Figures/StudyScale.png",
       height = 7, width = 12, bg='transparent')
```

@@

```{r Covariate quantity figure}
plot_covariateQuantity <- sheet_Covariates |> 
  separate_longer_delim(Covariates, delim = ", ") |>
  separate_wider_delim(Covariates, delim = "_", 
                       names = c("Covariate", "Variation", 
                                 "Observation", "Relation"),
                       too_few = "align_start") |>
  separate_wider_delim(Covariate, delim = "-",
                       names = c("Category", "Covariate"),
                       too_few = "align_start") |>
  filter(`Parameter type` %in% c("Initial occupancy", "Occupancy",
                                 "Colonisation", "Extinction_Persistence",
                                 "Detection")) |>
  summarise(Covariates = n(),
            .by = c(`Review ID`, `Model ID`, `Parameter type`, Category)) |>
  complete(nesting(`Review ID`, `Model ID`, `Parameter type`), 
           Category, fill = list(Covariates = 0)) |>
  filter(Category != "None") |>
  mutate(`Parameter type` = case_when(`Parameter type` == "Extinction_Persistence" ~ "Extinction",
                                      `Parameter type` == "Occupancy" ~ "Occupancy*",
                                      .default = `Parameter type`)) |>
  mutate(Parameter = fct(`Parameter type`, 
                         levels = c("Initial occupancy", "Occupancy*",
                                    "Colonisation", "Extinction",
                                    "Detection"))) |>
  mutate(Covariates = case_when(Covariates >= 15 ~ 15,
                                .default = Covariates)) |>
  mutate(Outlier = case_when(Covariates == 15 ~ TRUE,
                             .default = FALSE)) |>

  ggplot(aes(x = Category, y = Covariates)) +
  geom_boxplot(aes(fill = Category), 
               outliers = TRUE, linewidth = .3, staplewidth = 0.33,
               colour = "gray25") +
  scale_fill_manual("", labels = c("Environmental covariates", "Structural covariates"),
                    values = c("#4D7668", "plum4")) +
  scale_colour_manual("", labels = c("Environmental covariates", 
                                     "Structural covariates"),
                      values = c("#4D7668", "plum4")) +
  scale_y_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  labs(x = "", y = "Number of covariates\nconsidered") +
  facet_grid(cols = vars(Parameter), switch = "x") +
  guides(shape = "none") +
  theme(legend.position = "top",
        legend.box.margin = margin(-5,-10,-10,-10),
        legend.key.size = unit(12.5, 'points'),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        #panel.background = element_rect(fill = "gray80"),
        strip.text = element_text(size = 7.5, family = "Helvetica", colour = "#585858"), 
        axis.title.y = element_text(size = 8, family = "Helvetica", colour = "#585858"), 
        axis.text = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        legend.text = element_text(size = 8, family = "Helvetica", colour = "#585858"))

plot_covariateQuantity
ggsave(plot = plot_covariateQuantity, filename = "Figures/CovParamPlot.png",
       width = 1476, height = 700, units = "px")
```

@@

write_csv(table_covariateSummary, "Figures/CovariateTable.csv")
```

@@

write_csv(modelling_summary, "Figures/ModellingSummary.csv")
```

@@

  ggplot(aes(y = Covariate, x = PctComplex, fill = Cat_Complex)) +
  geom_col(colour = "white", 
           linewidth = 1, width = 1) +
  scale_fill_manual(limits = c("AnyTRUE", "EnvironmentalTRUE", "StructuralTRUE",
                               "AnyFALSE", "EnvironmentalFALSE", "StructuralFALSE"), 
                    values = c("goldenrod", "#4D7668", "plum4",
                               "gray80", "gray80", "gray80")) +
  scale_x_continuous(expand = c(0,0), breaks = c(25,50,75)) +
  facet_grid(rows = vars(Category), scales = "free_y",
             space = "free_y", switch = "y") +
  labs(x = "", y = "", title = "Average rate non-linear\nor interactive:") +
  theme(legend.position = "none",
        plot.background = element_blank(),
        panel.grid = element_blank(),
        axis.text.y = element_text(family = "Helvetica"), 
                                   #angle = 90, vjust = 0.5, hjust = 1),
        strip.text.y = element_blank(), 
        strip.background = element_blank(),
        strip.placement = "outside")
covariateComplex
```

@@

```{r Covariate_Patchwork}
covariatePatchwork <- covariateFreq + covariateDyn + covariateObs + covariateComplex +
  plot_layout(ncol = 4, axes = "collect") &
  theme(axis.text = element_text(size = 8, family = "Helvetica", colour = "#585858",
                                 face = "italic"),
        axis.title = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        plot.title = element_text(size = 8, family = "Helvetica", 
                                  colour = "#585858", hjust = 0.5)) 
covariatePatchwork

ggsave(plot = covariatePatchwork, "Figures/CovariateSummary.png",
       width = 1961, height = 1600, units = "px")
```

@@

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PctArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual("",
                    values = c("plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80),
                     limits = c(0, 80),
                     labels = c("0%", "20%", "40%", "60%", "80%")) +
  labs(y = "Percentage of studies\nwith objective", x = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15), axis.title = element_text(size = 15),
        legend.position = "bottom", strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_grid(cols = vars(Strata),
             scales = "free_x", space = "free_x", drop = TRUE)
plot_objectiveTrend
ggsave(plot = plot_objectiveTrend, "Figures/ObjectiveTrend.jpeg",
       width = 8, height = 4)
```

We render a second figure for the average number of covariates used in articles approaching each objective

```{r Covariates per objective}
#| fig-width: 8
#| fig-height: 4

covsPerParam <- sheet_Covariates |>
  mutate(studyID = paste(`Review ID`, `Model ID`, sep = "_")) |>
  separate_longer_delim(Covariates, delim = ", ") |>
  filter(`Parameter type` %in% c("Initial occupancy", "Occupancy",
                                 "Colonisation", "Extinction_Persistence",
                                 "Detection")) |>
  mutate(n_params = length(unique(`Parameter type`)),
         .by = c(studyID, `Review ID`)) |>
  filter(Covariates != "None") |>
  summarise(CovsPerParam = n()/max(n_params), 
            .by = c(studyID, `Review ID`))

plot_objectiveCovariates <- sheet_Objectives |>
  pivot_longer(c("Demonstrate methods?", "Estimate trends?", 
                 "Identify drivers?", "Test relationships?",
                 "Predict spatially?", "Predict temporally?"),
               names_to = "Objective", values_to = "ObjectiveIncluded") |>
  mutate(Objective = str_replace(Objective, "\\?", "")) |>
  filter(ObjectiveIncluded == "YES") %>%
  rbind(., mutate(., Objective = "Any Objective")) |>
  select(`Review ID`, Objective) |>
  distinct() |>
  left_join(covsPerParam, by = join_by(`Review ID`), relationship = "many-to-many") |>
  mutate(CovsPerParam = case_when(is.na(CovsPerParam) ~ 0,
                                  .default = CovsPerParam)) |>
  mutate(Objective = factor(Objective, levels = c("Any Objective", 
                                                  "Demonstrate methods",
                                                  "Estimate trends", 
                                                  "Identify drivers", 
                                                  "Test relationships",
                                                  "Predict spatially",
                                                  "Predict temporally"))) |>
  mutate(Objective = fct_relabel(Objective, 
                                 ~ str_replace(.x, " ", "\n"))) |>
  mutate(facet = case_when(Objective == "Any\nObjective" ~ "left",
                           .default = "right")) |>
  mutate(CovsPerParam = case_when(CovsPerParam > 15 ~ 15,
                                  .default = CovsPerParam)) |>
  mutate(Outlier = case_when(CovsPerParam == 15 ~ TRUE,
                             .default = FALSE)) |>

  ggplot(aes(x = Objective, y = CovsPerParam, 
             fill = Objective, colour = Objective)) +
  geom_boxplot(colour = "gray50", alpha = 0.6, outliers = FALSE) +
  geom_jitter(aes(shape = Outlier), alpha = 0.4, width = 0.3, size = 2.5) +
  scale_y_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  scale_fill_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                               "Estimate\ntrends", "Identify\ndrivers", 
                               "Test\nrelationships", "Predict\nspatially",
                               "Predict\ntemporally"),
                    values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_colour_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                                 "Estimate\ntrends", "Identify\ndrivers", 
                                 "Test\nrelationships", "Predict\nspatially",
                                 "Predict\ntemporally"),
                      values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                                 "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_shape_manual(limits = c(TRUE, FALSE),
                     values = c(17, 16)) +
  labs(x = "", y = "Number of covariates\nconsidered per parameter") +
  facet_grid(cols = vars(facet), scales = "free_x", space = "free_x") +
  guides(shape = "none") +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15), axis.text = element_text(size = 13),
        axis.title = element_text(size = 15), strip.background = element_blank(),
        strip.text = element_blank()) 
plot_objectiveCovariates
ggsave(plot = plot_objectiveCovariates, "Figures/ObjectiveCovariates.jpeg",
       width = 8, height = 4)
```

Combine the objective plots

```{r combine objective plots}
#| fig-width: 12
#| fig-height: 8

plot_stackedObjectives <- plot_objectiveTrend / plot_objectiveCovariates +
   plot_annotation(tag_levels = 'A')
plot_stackedObjectives

ggsave(plot = plot_stackedObjectives, "Figures/ObjectiveFigure.jpeg",
       width = 12, height = 8)

@@

  ggplot(aes(x = `Year Strata`, y = SiteNumber)) +
  geom_boxplot(fill = "goldenrod", colour = "gray40", staplewidth = 0.4,
               linewidth = 0.2, , outlier.size = 0.2) +
  scale_y_log10() +
  labs(x = "", y = "Number of sites\n(log scale)",
       title = "Site quantity") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Sites
```

@@

  ggplot(aes(x = `Year Strata`, y = CovsPerParam)) +
  geom_boxplot(fill = "goldenrod", colour = "gray40", staplewidth = 0.4,
               linewidth = 0.2, outlier.size = 0.2) +
  scale_y_log10() +
  labs(x = "", y = "Covariates\nper parameter",
       title = "Covariates considered") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Covariates
```

@@

  ggplot(aes(x = `Year Strata`, y = PropMethod,
             colour = `Selection method`, group = `Selection method`)) +
  geom_line() +
  geom_point(size = 1) +
  labs(x = "", y = "Percentage of models",
       title = "Selection method (MLE*)") +
  scale_colour_manual("",
                      limits = c("A priori", "Candidate set", 
                                 "Sequential", "Simple"),
                      labels = c("A priori", "Candidate set",
                                 "Sequential", "Simple precursors"),
                      values = c("aquamarine4", "cadetblue3",
                                 "plum4", "goldenrod")) +
  guides(colour = guide_legend(nrow = 2,
                               override.aes = list(size = 0.5,
                                                   linewidth = 0.5))) +
  theme(legend.position = "top",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"),
        legend.title = element_text(size = 8, family = "Helvetica"), 
        legend.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Selection
```

>>>>

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("#4D7668", "gray50")) +
  scale_y_continuous(expand = c(0,0), limits = c(0, 65)) +
  scale_x_continuous(#limits = seq(2004, 2023, 1),
                     breaks = seq(2004, 2023, 4),
                     labels = seq(2004, 2023, 4)) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-5,-10),
        legend.position = "top", 
        legend.key.size = unit(10, 'points'),
        legend.direction = "vertical",
        axis.text.y = element_text(size = 10, family = "helvetica", colour = "#585858"),
        axis.text.x = element_text(size = 10, family = "helvetica", 
                                   colour = "#585858", angle = 60,
                                   vjust = 1, hjust = 1), 
        axis.title = element_text(size = 10, family = "helvetica", colour = "#585858"), 
        legend.text = element_text(size = 10, family = "helvetica", colour = "#585858"),
        strip.text.x = element_text(size = 10, family = "helvetica", colour = "#585858"))
plot_reviewCoverage
ggsave(plot = plot_reviewCoverage, "Figures/1_CoveragePlot.png",
       width = 945, height = 700, units = "px")
```

@@

ggsave("Figures/3a_StudyMap.eps", plot = plot_studyAreaMap,
       width = 85, height = 50, units = "mm", bg = "transparent")

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "#4D7668", colour = "white",
           width = 1, linewidth = .5) +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("< 1", "1 - 10", "10 - 10<sup>2</sup>",
                              "10<sup>2</sup> - 10<sup>3</sup>",
                              "10<sup>3</sup> - 10<sup>4</sup>",
                              "10<sup>4</sup> - 10<sup>5</sup>",
                              "10<sup>5</sup> - 10<sup>6</sup>",
                              "\\> 10<sup>6</sup>")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_markdown(size = 8, angle = 90,
                                       vjust = 0.5, hjust = 1,
                                       family = "Helvetica", colour = "#585858"),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
plot_studyAreaSize

ggsave("Figures/3b_StudyArea.eps",
       plot = plot_studyAreaSize, 
       width = 80, height = 45, units = "mm",
       bg='transparent')
```

@@

ggsave("Figures/3c_Taxa.eps",
       plot_focalTaxa, width = 95, height = 40, units = "mm",
       bg = "transparent")
```

@@

# Plot site quantity distribution
plot_siteQuantity <- sheet_DataCollection |>
  filter(`Site quantity` != "Unclear") |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(x = `Site quantity`),
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  scale_x_continuous(transform = "log10",
                     breaks = c(0, 10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 7500),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  labs(y = "Number of\nsites", x = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent',
                                        color = NA),
        plot.background = element_rect(fill = 'transparent', 
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   #vjust = .5,
                                   hjust = 1,
                                   colour = "#585858",
                                   family = "Helvetica"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.margin = margin(20,10,0,10),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                   family = "Helvetica"))
plot_siteQuantity
ggsave(plot = plot_siteQuantity, 
       filename = "Figures/3e_Sites.eps",
       height = 35, width = 110, units = "mm")

@@

  ggplot() +
  geom_histogram(aes(x = StudyMonths), 
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(StudyMonths, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  labs(x = "", y = "Study\nduration") +
  scale_x_continuous(transform = "log10",
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years"),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent', 
                                        color = NA),
        plot.background = element_rect(fill = 'transparent',
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   hjust = 1, 
                                   family = "Helvetica",
                                   colour = "#585858"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                    family = "Helvetica"),
        plot.margin = margin(20,10,0,10))
plot_studyDuration
ggsave(plot = plot_studyDuration, 
       filename = "Figures/3e_Duration.eps",
       height = 35, width = 110, units = "mm",
       bg = "transparent")

# Calculate sample size
stat_studyDuration <- sheet_DataCollection |>
  filter(`Start month` != "Unclear" & `End month` != "Unclear") |>
  nrow()
stat_studyDuration
```

#### Primary occasions

```{r Primary occasions}
stat_medianPrimary <- sheet_DataCollection |>
  pull(`Primary occasions`) |>
  median()
stat_medianPrimary

stat_primaryRange <- sheet_DataCollection |>
  pull(`Primary occasions`) |>
  range()
stat_primaryRange
```

@@

```{r Covariate quantity figure}

plot_covariateQuantity <- sheet_Covariates |> 
  separate_longer_delim(Covariates, delim = ", ") |>
  separate_wider_delim(Covariates, delim = "_", 
                       names = c("Covariate", "Variation", 
                                 "Observation", "Relation"),
                       too_few = "align_start") |>
  separate_wider_delim(Covariate, delim = "-",
                       names = c("Category", "Covariate"),
                       too_few = "align_start") |>
  filter(`Parameter type` %in% c("Initial occupancy", "Occupancy",
                                 "Colonisation", "Extinction_Persistence",
                                 "Detection")) |>
  summarise(Covariates = n(),
            .by = c(`Review ID`, `Model ID`, `Parameter type`, Category)) |>
  complete(nesting(`Review ID`, `Model ID`, `Parameter type`), 
           Category, fill = list(Covariates = 0)) |>
  filter(Category != "None") |>
  mutate(`Parameter type` = case_when(`Parameter type` == "Extinction_Persistence" ~ "Extinction",
                                      `Parameter type` == "Occupancy" ~ "Occupancy*",
                                      `Parameter type` == "Initial occupancy" ~ "Initial\noccupancy",
                                      .default = `Parameter type`)) |>
  mutate(Parameter = fct(`Parameter type`, 
                         levels = c("Initial\noccupancy", "Occupancy*",
                                    "Colonisation", "Extinction",
                                    "Detection"))) |>
  mutate(Covariates = case_when(Covariates >= 15 ~ 15,
                                .default = Covariates)) |>
  mutate(Outlier = case_when(Covariates == 15 ~ TRUE,
                             .default = FALSE)) |>

  ggplot(aes(x = Category, y = Covariates)) +
  geom_boxplot(aes(fill = Category), 
               outliers = TRUE, linewidth = .3, staplewidth = 0.33,
               colour = "gray25") +
  scale_fill_manual("", labels = c("Environmental covariates", "Structural covariates"),
                    values = c("#4D7668", "plum4")) +
  scale_colour_manual("", labels = c("Environmental covariates", 
                                     "Structural covariates"),
                      values = c("#4D7668", "plum4")) +
  scale_y_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  labs(x = "", y = "Number of covariates\nconsidered") +
  facet_grid(cols = vars(Parameter), switch = "x") +
  guides(shape = "none") +
  theme(legend.position = "top",
        legend.box.margin = margin(-5,-10,-10,-10),
        legend.key.size = unit(12.5, 'points'),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        #panel.background = element_rect(fill = "gray80"),
        strip.text = element_text(size = 10, family = "Helvetica", colour = "#585858"), 
        axis.title.y = element_text(size = 10, family = "Helvetica", colour = "#585858"), 
        axis.text = element_text(size = 10, family = "Helvetica", colour = "#585858"),
        legend.text = element_text(size = 10, family = "Helvetica", colour = "#585858"))

plot_covariateQuantity
ggsave(plot = plot_covariateQuantity, filename = "Figures/5_CovariateCount.png",
       width = 1476, height = 700, units = "px")
```

@@

write_csv(table_covariateSummary, "Figures/S1_CovariateTable.csv")
```

@@

write_csv(modelling_summary, "Figures/T2_ModellingSummary.csv")
```

@@

  ggplot(aes(y = Covariate, x = PctComplex, fill = Cat_Complex)) +
  geom_col(colour = "white", 
           linewidth = 1, width = 1) +
  scale_fill_manual(limits = c("AnyTRUE", "EnvironmentalTRUE", "StructuralTRUE",
                               "AnyFALSE", "EnvironmentalFALSE", "StructuralFALSE"), 
                    values = c("goldenrod", "#4D7668", "plum4",
                               "gray80", "gray80", "gray80")) +
  scale_x_continuous(expand = c(0,0), breaks = c(25,50,75)) +
  facet_grid(rows = vars(Category), scales = "free_y",
             space = "free_y", switch = "y") +
  labs(x = "", y = "", title = "Average rate\nnon-linear or interactive:") +
  theme(legend.position = "none",
        plot.background = element_blank(),
        panel.grid = element_blank(),
        axis.text.y = element_text(family = "Helvetica"), 
                                   #angle = 90, vjust = 0.5, hjust = 1),
        strip.text.y = element_blank(), 
        strip.background = element_blank(),
        strip.placement = "outside")
covariateComplex
```

@@

```{r Covariate_Patchwork}
covariatePatchwork <- covariateFreq + covariateDyn + covariateObs + covariateComplex +
  plot_layout(ncol = 4, axes = "collect") &
  #plot_annotation(tag_levels = 'a', tag_prefix = '(', tag_suffix = ")") &
  theme(axis.text = element_text(size = 8, family = "Helvetica", colour = "#585858",
                                 face = "italic"),
        axis.title = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        plot.title = element_text(size = 8, family = "Helvetica", 
                                  colour = "#585858", hjust = 0.5),
        plot.tag = element_text(size = 9, family = "Helvetica", colour = "#585858")) 
covariatePatchwork

#ggsave(plot = covariatePatchwork, "Figures/4_CovariateSummary.png",
#       width = 1961, height = 1600, units = "px")
```

@@

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PctArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual("",
                    values = c("plum4", "cadetblue3", "aquamarine3",
                               "#4D7668", "goldenrod", "goldenrod4")) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80),
                     limits = c(0, 80),
                     labels = c("0%", "20%", "40%", "60%", "80%")) +
  labs(y = "Percentage of studies\nwith objective", x = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.text = element_text(size = 9, family = "helvetica", colour = "#585858"),
        axis.text = element_text(size = 9, family = "helvetica", colour = "#585858"), 
        axis.title = element_text(size = 9, family = "helvetica", colour = "#585858"),
        legend.box.margin = margin(-5,-10,-10,-10),
        legend.key.size = unit(12.5, 'points'),
        legend.position = "top", 
        strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_grid(cols = vars(Strata),
             scales = "free_x", space = "free_x", drop = TRUE)
plot_objectiveTrend
ggsave(plot = plot_objectiveTrend, "Figures/2_Objectives.png",
       width = 1476, height = 700, units = "px")
```

@@

  ggplot(aes(x = `Year Strata`, y = SiteNumber)) +
  geom_boxplot(fill = "#4D7668", 
               linewidth = .3, staplewidth = 0.33,
               colour = "gray25") +
  scale_y_log10(breaks = c(10,100,1000,10000), limits = c(10,10000)) +
  labs(x = "", y = "Number of sites\n(log)",
       title = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Sites
```

@@

  ggplot(aes(x = `Year Strata`, y = CovsPerParam)) +
  geom_boxplot(fill = "#4D7668", linewidth = .3, staplewidth = 0.33,
               colour = "gray25") +
  scale_y_log10() +
  labs(x = "", y = "Covariates per\nparameter (log)",
       title = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Covariates
```

@@

  ggplot(aes(x = `Year Strata`, y = PropMethod,
             colour = `Selection method`, group = `Selection method`)) +
  geom_line() +
  geom_point(size = 1) +
  labs(x = "", y = "Percentage of\nmodels",
       title = "") +
  scale_colour_manual("",
                      limits = c("A priori", "Candidate set", 
                                 "Sequential", "Simple"),
                      labels = c("A priori", "Candidate set",
                                 "Sequential", "Simple precursors"),
                      values = c("#4D7668", "cadetblue3",
                                 "plum4", "goldenrod")) +
  guides(colour = guide_legend(nrow = 2,
                               override.aes = list(size = 1,
                                                   linewidth = 1))) +
  theme(legend.position = "top",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        axis.title = element_text(size = 8, family = "Helvetica"), 
        axis.text = element_text(size = 8, family = "Helvetica"),
        legend.title = element_text(size = 8, family = "Helvetica"), 
        legend.text = element_text(size = 8, family = "Helvetica"))
timeSeries_Selection
```
